---
title: "EPI 590R Final Project"
author: "Shamika Chavda"
date: '2024-09-04'
format: html
---

**Dataset:** *worlds_fairs* -- Data about fairs/expositions held globally with data on cost, attendance, location, type, etc. Found here: https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-08-13/readme.md

**Loading packages & dataset**

```{r}
##Load packages
library(tidyverse)
library(gtsummary)
library(here)

#Load dataset
world_fairs <- read.csv(here("./data/worlds_fairs.csv"))

#Code for inline statistic
stats <- list(n = nrow(world_fairs),
							mean_attendance = mean(world_fairs$visitors))
```

There were `r stats$n` fairs included in the dataset, with a mean attendance of `r stats$mean_attendance`.

**Creating table with descriptive statistics**

```{r}
#| label: tbl-one
#| tbl-cap: "Table of descriptive statistics"
head(worlds_fairs)
tbl_summary(
world_fairs,
	by="category",
	include = c(country, visitors, cost),
	label = list(
		country ~ "Country",
		visitors ~ "Visitors",
		cost ~ "Cost"),
	statistic = list(
		visitors ~ c("{p25},{p75}({median})"),
		cost ~ c("{p25},{p75}({median})"))) |>
	bold_labels()

```

**Creating univariate regression table**

```{r}
#| label: tbl-two
#| tbl-cap: "Univariate regression table"
tbl_uvregression(
	world_fairs,
	y = cost,
	include = c(country, category, visitors, cost),
	method = lm
	)
```

**Creating histogram of fair attendance**

```{r}
#| label: fig-hist
#| fig-cap: "Histogram of fair attendance"
hist(world_fairs$visitors,
		 main="Attendance to Fairs, Globally",
		 xlab="Visitors",
		 col="orange",
		)
png(file=here::here("Attendance_Fairs.png"))
```
