---
title: "EPI 590R Final Project"
author: "Shamika Chavda"
date: '2024-09-04'
format: html
---

**Loading packages & dataset**

```{r}
#| echo: false
#| message: false
##Load packages
library(tidyverse)
library(gtsummary)
library(here)
```

```{r}
#Load dataset
world_fairs <- read.csv(here("./data/worlds_fairs.csv"))

#Code for inline statistic
stats <- list(n = nrow(world_fairs),
							mean_attendance = mean(world_fairs$visitors, na.RM = TRUE))
```

**Dataset:** *worlds_fairs* -- Data about fairs/expositions held globally with 
data on cost, attendance, location, type, etc. 
Found here: https://github.com/rfordatascience/tidytuesday/blob/master/data/2024/2024-08-13/readme.md

There were `r stats$n` fairs included in the dataset.

**Creating table with descriptive statistics**

```{r}
#| label: tbl-one
#| tbl-cap: "Table of descriptive statistics"
tbl_summary(
world_fairs,
	by="category",
	include = c(country, visitors, cost),
	label = list(
		country ~ "Country",
		visitors ~ "Visitors",
		cost ~ "Cost"),
	statistic = list(
		visitors ~ c("{p25},{p75}({median})"),
		cost ~ c("{p25},{p75}({median})"))) |>
	bold_labels()

```

**Creating univariate regression table**

```{r}
#| label: tbl-two
#| tbl-cap: "Univariate regression table"

tbl_uvregression(
	world_fairs,
	y = cost,
	include = c(country, category, visitors, cost),
	method = lm,
	label = list(
		country ~ "Country",
		category ~ "Category",
		visitors ~ "Visitors"
	)
	)
#Create object for inline text
cost_table <- 
	tbl_uvregression(
	world_fairs,
	y = cost,
	include = c(country, category, visitors, cost),
	method = lm,
	label = list(
		country ~ "Country",
		category ~ "Category",
		visitors ~ "Visitors"
	)
	)

inline_text(cost_table, variable="visitors")
```

**Creating histogram of fair attendance**

```{r}
#| label: fig-hist
#| fig-cap: "Histogram of fair attendance"
#| message: false
visitors_hist <- hist(world_fairs$visitors,
		 main="Attendance to Fairs, Globally",
		 xlab="Visitors",
		 col="orange",
		)

pdf(here::here("Figures","visitors_hist.pdf"))
dev.off()
```
@fig-hist contains a histogram, @tbl-one shows descriptive statistics,
and @tbl-two shows the regression table. 

**Create function for standard deviation**

```{r}
sd_function <- function(x, multiplier =1) {
	n <- length(x)
	mean_val <-sum(x, na.rm=TRUE)/n
	sd_val <- sqrt(sum(!is.na(x-mean_val)^2) / (n-1))
	return(sd_val)
}
sd_function(world_fairs$cost)

```
